R for Clinical Study Reports and Submission

### 2021-09-02 tlf-ae-summary.Rmd
update ch7 `t_pop` code

```{r}
t_pop <- adsl %>%
  filter(SAFFL == "Y") %>%
  count_by("TRT01AN", "SAFFL",
    var_label = "Participants in population"
  ) %>%
  rename(name = var_label) %>%
  select(name, starts_with("n_"))

>>>>

```{r}
t_pop <- pop %>% 
  mutate(name = "Participants in population", 
         tot = fmt_num(tot, digits = 0)) %>% 
  pivot_wider(id_cols = name, 
              names_from = TRTAN, 
              names_prefix = "n_", 
              values_from = tot)
